---
title: "learn R markdown"
author: "Zijun"
date: "11/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

superscript^2^ and subscript~2~

* Bulleted list item 1
* Item 2
    * Item 2a
    * item 2b
    
1. Numbered list item 1
1. Item 
1. The numbers are incremented automatically in the output.

[R markdown Basics](https://rmarkdown.rstudio.com/authoring_basics.html)

Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

```{r section1}
mtcars[1:5, ]
```
```{r section2}
knitr::kable(
  mtcars[1:5, ], 
  caption = "A knitr kable."
)
```

Normally, each knit of a document starts from a completely clean slate. This is great for reproducibility, because it ensures that you’ve captured every important computation in code. However, it can be painful if you have some computations that take a long time. The solution is `cache = TRUE`. 

## Inline code

```{r}
comma <- function(x) format(x, digits = 2, big.mark = ",")
comma(1234567)
comma(0.234567)
```
                                                                                                                                                                                                                                                                                                                                                                                                                                                     

